---
title: "Teaching data science authentically"
subtitle: "using open source educational resources"  
author: 
  - "Tiffany A. Timbers"
date: '`r Sys.Date()`'
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: xaringan-themer.css
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_duo_accent(
  primary_color = "#1381B0",
  secondary_color = "#FF961C",
  inverse_header_color = "#FFFFFF"
)
```


# Why use Open Educational Resources in Teaching?

(in general)

---

# Why use Open Educational Resources in Teaching?

(in data science specifically)

---

# Role of Open Source in Data Science

---

# Using Data Science Open Source tools in Teaching

Practice what you preach!

---

# Example of OER's built using Data Science Open Source tools

1. [*Data Science: A First Introduction*](https://ubc-dsci.github.io/introduction-to-datascience/) - an open textbook aimed at undergraduates students taking their first course in data science

2. [Syllabi, lecture notes, labs and lecture videos from courses for a professional Master's in Data Science program](https://github.com/UBC-MDS/public)

3. [Key Capabilities in Data Science online courses](https://extendedlearning.ubc.ca/programs/key-capabilities-data-science) - Interactive online learning modules aimed at mid-career learners

---

# *Data Science: A First Introduction*

- aimed at first year undergraduates, from any discipline, no pre-req knowledge needed
- created via R + `bookdown`
- openly available HTML version on the web (always)
- partnering with CRC Press to publish a print version (paid)

---

# UBC MDS syllabi, lecture notes, labs & lecture videos

- course resources from a Master of Data Science program
- program uses OER's from others, as well as creates its own
- syllabi and course notes created via Jupyter, R Markdown & hosted on GitHub
- videos of some courses hosted on YouTube

---

# Key Capabilities in Data Science online courses

- suite of online courses, and a certificate program, aimed at mid-career learners in British Columbia, Canada, but open to anyone
- paid version of the courses includes a course facilitator, office hours, graded assignments and quizzes
- course notes, videos and knowledge checks are openly available 
- open content created via Ines Montani's open course framework, whose front-end is powered by Gatsby and Reveal.js and back-end code execution is powered by BinderHub

#### Open course content:

- [Programming in Python for Data Science](https://prog-learn.mds.ubc.ca)
- [Data Visualization](https://viz-learn.mds.ubc.ca/)
- [Introduction to Machine Learning](https://ml-learn.mds.ubc.ca/en)

---

# Lessons learned from Building Data Science OER's

- don't do it alone

---

# Lessons learned from Sharing Data Science OER's

- don't be afraid to share
- use a license

---

# Lessons learned from Maintaining Data Science OER's

- maintenance is needed to keep material current
- OER's which need interactive computation require money or infrastructure to share

---

# Impact of OER's

---

# Attribution

---

# Resources

--- 

# Thanks

---
