---
title: "Teaching data science authentically"
subtitle: "using open source educational resources"  
author: 
  - "Tiffany A. Timbers"
date: '`r Sys.Date()`'
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: xaringan-themer.css
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_duo_accent(
  primary_color = "#1381B0",
  secondary_color = "#FF961C",
  inverse_header_color = "#FFFFFF"
)
```


# Why use Open Educational Resources in Teaching?

(in general)

---

# Why use Open Educational Resources in Teaching?

(in data science specifically)

---

# Role of Open Source in Data Science

---

# Using Data Science Open Source tools in Teaching

Practice what you preach!

---

# Example of OER's built using Data Science Open Source tools

1. [*Data Science: A First Introduction*](https://ubc-dsci.github.io/introduction-to-datascience/) - an open textbook aimed at undergraduates students taking their first course in data science

2. [Syllabi, lecture notes, labs and lecture videos from courses for a professional Master's in Data Science program](https://github.com/UBC-MDS/public)

3. [Key Capabilities in Data Science online courses](https://extendedlearning.ubc.ca/programs/key-capabilities-data-science) - Interactive online learning modules aimed at mid-career learners

---

# *Data Science: A First Introduction*

---

# UBC MDS syllabi, lecture notes, labs & lecture videos

---

# Key Capabilities in Data Science online courses

---

# Lessons learned from Building Data Science OER's

---

# Lessons learned from Maintaining Data Science OER's

---

# Impact of OER's

---

# Attribution

---

# Resources

--- 

# Thanks

---
